Meta RL analyses

### 2018-10-23 meta_RL_analyses.Rmd
I swear I already committed these bugfixes??

```{r}
for (emb_type in c("guess", "final")) {
  emb_d = data.frame()
  for (run_i in 0:(nruns-1)) {
    filename = sprintf("%sm2l%s_run%i_%s_embeddings.csv", resulst_dir, run_i, emb_type)
    if (!file.exists(filename)) {
      next
    }
    this_d = read.csv(filename, header=T)
    this_d$run = run_i
    emb_d = bind_rows(emb_d, this_d)
  }

  pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
  pc_d = data.frame(pcs$rotation)
  pc_d$task = row.names(pc_d)
  ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
    geom_point() +
    geom_text(aes(label=task)) +
    guides(color=F)
  ggsave(sprintf("plots/PCA_full_%s.png", results_dir, emb_type), width=7, height=7)
}
```

```{r}
emb_type = "guess"
emb_d = data.frame()
for (meta_task in c("None", meta_mapping_tasks)) {
  for (run_i in 0:(num_runs-1)) {
    if (meta_task == "None") {
      filename = sprintf("%srun%i_%s_embeddings.csv",results_dir, run_i, emb_type)
      if (!file.exists(filename)) {
#          print(paste("Skipping", filename, sep=" "))
        next 
      }
      this_d = read.csv(filename, header=T)
    } else {
      filename = sprintf("%srun%i_%s_%s_embeddings.csv", results_dir, run_i, meta_task, emb_type)
      if (!file.exists(filename)) {
#          print(paste("Skipping", filename, sep=" "))
        next 
      }
      this_d = read.csv(filename, header=T)
    }
    this_d$run = run_i
    this_d$meta_task = meta_task
    emb_d = bind_rows(emb_d, this_d)
  }
}
```

>>>>

```{r}
for (emb_type in c("guess", "final")) {
  emb_d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    filename = sprintf("%srun%i_%s_embeddings.csv", results_dir, run_i, emb_type)
    if (!file.exists(filename)) {
      next
    }
    this_d = read.csv(filename, header=T)
    this_d$run = run_i
    emb_d = bind_rows(emb_d, this_d)
  }

  pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
  pc_d = data.frame(pcs$rotation)
  pc_d$task = row.names(pc_d)
  ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
    geom_point() +
    geom_text(aes(label=task)) +
    guides(color=F)
  ggsave(sprintf("plots/PCA_full_%s.png", emb_type), width=7, height=7)
}
```

```{r}
# emb_type = "guess"
# emb_d = data.frame()
# for (meta_task in c("None", meta_mapping_tasks)) {
#   for (run_i in 0:(num_runs-1)) {
#     if (meta_task == "None") {
#       filename = sprintf("%srun%i_%s_embeddings.csv",results_dir, run_i, emb_type)
#       if (!file.exists(filename)) {
# #          print(paste("Skipping", filename, sep=" "))
#         next 
#       }
#       this_d = read.csv(filename, header=T)
#     } else {
#       filename = sprintf("%srun%i_%s_%s_embeddings.csv", results_dir, run_i, meta_task, emb_type)
#       if (!file.exists(filename)) {
# #          print(paste("Skipping", filename, sep=" "))
#         next 
#       }
#       this_d = read.csv(filename, header=T)
#     }
#     this_d$run = run_i
#     this_d$meta_task = meta_task
#     emb_d = bind_rows(emb_d, this_d)
#   }
# }
```
